---
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r}
library(sas7bdat)
library(dplyr)
library(reshape2)
library(ggplot2)
library(ggthemes)
library(survival)
library(survminer)
library(zoo)
```

### Reading data
```{r}
Data <- read.sas7bdat("/Users/dauku/Desktop/Courses/2019Fall/Survival/Homework1_SA/hurricane.sas7bdat")
Data$reason <- as.factor(Data$reason)
```

### Summary statistics fro each of the types of pump station failure:
```{r}
# percentage of pumps that survived the hurricane
NotSurvived <- Data %>% filter(survive == 1)
PercentSurvived <- nrow(NotSurvived)/nrow(Data)*100
PercentSurvived

# percentage of pumps in wach type of failure
FailurePct <- Data %>%
  group_by(reason) %>%
  summarise(Pct = n()/nrow(Data))

# average failure time for each failure type
AvgFailure <- Data %>%
  group_by(reason) %>%
  summarise(Avg = mean(hour), Median = median(hour))

# Statistical test if these averages for each type of failure are different
ANOVA <- aov(hour ~ reason, data = Data)
summary(ANOVA)

# From the ANOVA we can tell that the p-value is really small which implies that at least one type of failure is different to others
TukeyHSD(ANOVA)
# According to Tukey's test, only the difference between type3 and type2 is insignificant
```

### Survival probability across time for all pumps together
```{r}
# Creating survival object
Together <- survfit(Surv(time = hour, event = (survive == 0)) ~ 1, data = Data)
summary(Together)

TogetherPlot <- merge(
  data.frame(time = seq(1, 48, 1)),
  data.frame(time = Together$time, SP = Together$surv),
  by = "time", all = TRUE)

# Impute the values for the missing time
TogetherPlot <- na.locf(TogetherPlot)
TogetherPlot[is.na(TogetherPlot)] <- 1

# Visualize the survival probability
ggplot(TogetherPlot)+ geom_line(aes(x = time, y = SP), size = 1, color = '#8dd3c7') + scale_y_continuous(limits = c(0, 1)) +
  labs(title =  'Overall Survival Probability',
       y = "Survival Probability",
       x = "Hours") + theme_hc(base_size = 10)+
  theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust= 0.5),legend.title=element_blank())
```

### Survival probability across time for pumps broken down by failure type overlaid into one graph
```{r}
# Subset the data
Reason1 <- Data %>% filter(reason == 1)
Reason2 <- Data %>% filter(reason == 2)
Reason3 <- Data %>% filter(reason == 3)
Reason4 <- Data %>% filter(reason == 4)
Subsets <- list(Reason1, Reason2, Reason3, Reason4)

# Prepare the data for visualization
SurvivalP <- data.frame(time = seq(1, 48, 1))
for (i in seq(1, 4)) {
  SurvivalModel <- survfit(Surv(time = hour, event = (survive == 0)) ~ 1, data = Subsets[[i]])
  ModelDF <- data.frame(time = SurvivalModel$time, s = SurvivalModel$surv)
  ColName <- paste0("Reason", as.character(i), collapse = "")
  colnames(ModelDF) <- c("time", ColName)
  S <- merge(data.frame(time = seq(1, 48, 1)),
               ModelDF,
               by = "time", all = TRUE)
  S <- na.locf(S)


  SurvivalP <- left_join(SurvivalP, S, by = "time")
}

SurvivalP[is.na(SurvivalP)] <- 1


# Plotting survival curves for each failure reason
SurvivalCurves = melt(SurvivalP, id.vars = "time", measure.vars = c("Reason1", "Reason2", "Reason3", "Reason4"))

ggplot(SurvivalCurves)+ geom_line(aes(x = time, y = value, color = variable), size = 1)+
  scale_colour_manual(values = c('#4daf4a','#e41a1c', "#377eb8", "#984ea3"),labels = c('Flood', 'Motor', 'Surge', 'Jammed'))+

  labs(title =  'Survival Probability by Failure Reason',
       y = "Survival Probability",
       x = "Hours") + theme_hc(base_size = 10)+
  theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust= 0.5),legend.title=element_blank())
```

### Conditional failure probabilities across time for all pumps together
```{r}
# Calculate the hazard probabilities
Together$hp <- Together$n.event/Together$n.risk
TogetherHaz <- data.frame(Time = seq(1, 48, 1), hp = Together$hp)

# Visualize the overall conditional failure probability
ggplot(TogetherHaz)+ geom_line(aes(x = Time, y = hp), size = 1, color = '#8dd3c7') +
  labs(title =  'Overall Hazard Probability',
       y = "Hazard Probability",
       x = "Hours") + theme_hc(base_size = 10)+
  theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust= 0.5),legend.title=element_blank())
```

### Conditional failure probabilities across time break down by failure types
```{r}
# Subset data
Reason1 <- Data %>% filter(reason == 1)
Reason2 <- Data %>% filter(reason == 2)
Reason3 <- Data %>% filter(reason == 3)
Reason4 <- Data %>% filter(reason == 4)
Subsets <- list(Reason1, Reason2, Reason3, Reason4)

# Make the data for visualization
HazFinal <- data.frame(time = seq(1, 48, 1))

for (i in seq(1, 4)) {
  HazModel <- survfit(Surv(time = hour, event = (survive == 0)) ~ 1, data = Subsets[[i]])
  HazModel$hp <- HazModel$n.event/HazModel$n.risk
  
  HazValue <- data.frame(time = HazModel$time, hp = HazModel$hp)
  ColName <- paste0("Reason", as.character(i), collapse = "")
  colnames(HazValue) <- c("time", ColName)
  
  Haz <- merge(data.frame(time = seq(1, 48, 1)),
               HazValue,
               by = "time", all = TRUE)
  Haz[is.na(Haz) == TRUE] <- 0
  
  
  HazFinal <- left_join(HazFinal, Haz, by = "time")
}


# Visualization
library(reshape2)
HazEachReason = melt(HazFinal, id.vars = "time", measure.vars = c("Reason1", "Reason2", "Reason3", "Reason4"))

ggplot(HazEachReason)+ geom_line(aes(x = time, y = value, color = variable), size = 1)+
  scale_colour_manual(values = c('#4daf4a','#e41a1c', "#377eb8", "#984ea3"),labels = c('Flood', 'Motor', 'Surge', 'Jammed'))+

  labs(title =  'Hazard Probability by Reason',
       y = "Hazard Probability",
       x = "Hours") + theme_hc(base_size = 10)+
  theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust= 0.5),legend.title=element_blank())
```


### Test if the major types of failure have similar survival probabilities across time
```{r}
# Water-based: flood and surge have the same survival curve?
survdiff(Surv(time = hour, event = (survive == 0)) ~ reason, rho = 1, data = Data)

Failed = Data %>% filter(reason == 1 | reason == 2 | reason == 3 | reason == 4)

# Pairwise survival curve comparision
# Wilcox
pairwise_survdiff(Surv(time = hour, event = (survive == 0)) ~ reason, data = Failed, p.adjust.method = "bonferroni", rho = 1)

# Log-rank
pairwise_survdiff(Surv(time = hour, event = (survive == 0)) ~ reason, data = Failed, p.adjust.method = "bonferroni", rho = 0)
```
