---
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r}
library(sas7bdat)
library(dplyr)
library(reshape2)
library(ggplot2)
library(ggthemes)
library(survival)
library(survminer)
library(zoo)
library(flexsurv)
```

### Reading data
```{r}
Data <- read.sas7bdat("/Users/dauku/Desktop/Courses/2019Fall/Survival/Homework1_SA/hurricane.sas7bdat")
Data$reason <- as.factor(Data$reason)
Data$pumpid <- seq(1, nrow(Data))
Data$Flood <- sapply(Data$reason, function(x) {
  if (x == 1) {
    return(1)
  } else {
    return(0)
  }
})
```

### Here is just I want to make the cummulative hazard fuction fancier, not finished yet
```{r}
# red line
WeibullCurve <- flexsurvreg(Surv(hour, Flood == 1) ~
                           backup + age + bridgecrane + servo + gear + trashrack + slope + elevation,
                         data = Data, dist = "weibull")
WeibullRed <- summary(WeibullCurve, type = "cumhaz", ci = TRUE, tidy = TRUE)
WeibullCurve$dlist

WeibullKM <- survfit(Surv(hour, Flood == 1) ~ 1,
                         data = Data, type = "kaplan-meier", conf.type = "log")$cumhaz

Plotting = WeibullRed %>% dplyr::select(1:4)
Plotting$cumhaz = WeibullKM

Cumhaz = data.frame(time = seq(1, 48), Cumhaz = WeibullKM)
Cum = melt(Cumhaz, id.vars = "time", measure.vars = "Cumhaz")
Curves = melt(Plotting, id.vars = "time", measure.vars = c("est", "lcl", "ucl"))

ggplot(Curves)+ geom_line(aes(x = time, y = value, color = variable), size = 1)+
  scale_colour_manual(values = c('#4daf4a','#e41a1c', "#377eb8", "#984ea3"),labels = c('est', 'lcl', 'ucl', 'cumhaz'))+

  labs(title =  'Theoretical Weibull cumulative hazard function',
       y = "cumulative hazard probability",
       x = "Hours") + theme_hc(base_size = 10)+
  theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust= 0.5),legend.title=element_blank())

ggplot() + 
  geom_step(data=Cum,mapping=aes(x=time,y=value, color = variable),
            linetype="dashed") +
  geom_line(data=Curves,mapping=aes(x=time, y=value, color = variable),
            linetype=1) + ylab('Cumulative Hazard Function') + xlab('time') +  scale_colour_manual(values = c("black", "red",'#f1a340', '#f1a340'),labels = c("Actual-CHP", 'Estimated CHP', 'Confidence Interval', 'Confidence Interval'))+
  labs(title =  'Theoretical Weibull Cumulative Hazard Function',
       y = "Cumulative Hazard Probability",
       x = "Hours")+theme_classic(base_size = 18)+
  theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust= 0.5),legend.title=element_blank())
```

### Determine the appropriate distribution
```{r}
DistList = c("gamma", "exp", "weibull", "lnorm", "llogis")

for (dist in DistList) {
  Weibull <- flexsurvreg(Surv(hour, Flood == 1) ~
                           backup + age + bridgecrane + servo + gear + trashrack + slope + elevation,
                         data = Data, dist = dist)
  
  plot(Weibull, type = "cumhaz", ci = TRUE, conf.int = FALSE, las = 1, bty = "n",
       xlab = "Hour", ylab = "Cumulative Hazard", main = paste(dist, "Distribution", collapse = " "))
}
```
From the plots, we can tell exponential distribution is off a lot, so we will exclude exponential from our distrubution candidate list.

```{r}
# Calculate likelihood function for each distribution
LikeTestList <- c("gamma", "weibull", "lnorm", "llogis")
DistPvalues <- data.frame("Dist" = LikeTestList)
DistPvalues$like <- sapply(DistPvalues$Dist, function(x) {
  Model <- flexsurvreg(Surv(hour, Flood == 1) ~ 
                              backup + age + bridgecrane + servo + gear + trashrack + slope + elevation,
                         data = Data, dist = as.character(x))
  return(Model$loglik)
})

# Goodness-of-fit test
w.g <- 1 - pchisq((-2 * (as.numeric(DistPvalues %>% filter(Dist == "weibull") %>% select(like)) - as.numeric(DistPvalues %>% filter(Dist == "gamma") %>% select(like)))), 1)

ln.g <- 1 - pchisq((-2 * (as.numeric(DistPvalues %>% filter(Dist == "lnorm") %>% select(like)) - as.numeric(DistPvalues %>% filter(Dist == "gamma") %>% select(like)))), 1)
```
# From the statistical formal test we can conclude that gamma is better than log-normal, and weibull is better than gamma.

### Variable selection using backward selection
```{r}
Model1 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + age + bridgecrane + servo + gear + trashrack + slope + elevation, data = Data, dist = "weibull")
summary(Model1)

Model2 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + bridgecrane + servo + gear + trashrack + slope + elevation, data = Data, dist = "weibull")
summary(Model2)

Model3 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + servo + gear + trashrack + slope + elevation, data = Data, dist = "weibull")
summary(Model3)

Model4 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + servo + gear + trashrack + slope, data = Data, dist = "weibull")
summary(Model4)

Model5 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + servo + trashrack + slope, data = Data, dist = "weibull")
summary(Model5)

Model6 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + servo + slope, data = Data, dist = "weibull")
summary(Model6)
```
The most significant variable is slope. 45.4% decrease in the expected survival time for each one-unit increases in slope.

### Predicted Survial Probability at t
```{r}
survprob.actual <- 1 - psurvreg(Data$hour, mean = predict(Model6, type = "lp"),
                                scale = Model6$scale, distribution = Model6$dist)
```

### Predicted change in event time due to backup
```{r}
Backup <- qsurvreg(1 - survprob.actual, mean = predict(Model6, type = "lp") + coef(Model6)["backup"],
                   scale = Model6$scale, distribution = Model6$dist)
Data$t_backup <- Backup
Data$diff_backup <- Data$t_backup - Data$hour
```

### Predicted change in event time due to servo
```{r}
Servo <- qsurvreg(1 - survprob.actual, mean = predict(Model6, type = "lp") + coef(Model6)["servo"],
                   scale = Model6$scale, distribution = Model6$dist)
Data$t_servo <- Servo
Data$diff_servo <- Data$t_servo - Data$hour

Data2 <- Data %>% filter(Flood == 1)
```

### Select the best upgrade
```{r}
Upgrade <- Data %>% filter(Flood == 1)
Upgrade$Diff <- Upgrade$diff_servo - Upgrade$diff_backup

# upgrade list
UpgradeList <- Upgrade %>% arrange(desc(diff_servo)) %>% slice(1:16) %>% dplyr::select(pumpid, hour, t_servo, diff_servo)
UpgradeList %>% summarise(sum = sum(diff_servo))
```


