---
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r}
library(sas7bdat)
library(dplyr)
library(reshape2)
library(ggplot2)
library(ggthemes)
library(survival)
library(survminer)
library(zoo)
library(flexsurv)
```

### Reading data
```{r}
Data <- read.sas7bdat("/Users/dauku/Desktop/Courses/2019Fall/Survival/Homework1_SA/hurricane.sas7bdat")
Data$reason <- as.factor(Data$reason)
Data$Flood <- sapply(Data$reason, function(x) {
  if (x == 1) {
    return(1)
  } else {
    return(0)
  }
})
```

### Determine the appropriate distribution
```{r}
DistList = c("gamma", "exp", "weibull", "lnorm", "llogis")

for (dist in DistList) {
  Weibull <- flexsurvreg(Surv(hour, Flood == 1) ~
                           backup + age + bridgecrane + servo + gear + trashrack + slope + elevation,
                         data = Data, dist = dist)
  
  plot(Weibull, type = "cumhaz", ci = TRUE, conf.int = FALSE, las = 1, bty = "n",
       xlab = "Hour", ylab = "Cumulative Hazard", main = paste(dist, "Distribution", collapse = " "))
}
```
From the plots, we can tell exponential distribution is off a lot, so we will exclude exponential from our distrubution candidate list.

```{r}
# Calculate likelihood function for each distribution
LikeTestList <- c("gamma", "weibull", "lnorm", "llogis")
DistPvalues <- data.frame("Dist" = LikeTestList)
DistPvalues$like <- sapply(DistPvalues$Dist, function(x) {
  Model <- flexsurvreg(Surv(hour, Flood == 1) ~ 
                              backup + age + bridgecrane + servo + gear + trashrack + slope + elevation,
                         data = Data, dist = as.character(x))
  return(Model$loglik)
})

# Goodness-of-fit test
w.g <- 1 - pchisq((-2 * (as.numeric(DistPvalues %>% filter(Dist == "weibull") %>% select(like)) - as.numeric(DistPvalues %>% filter(Dist == "gamma") %>% select(like)))), 1)

ln.g <- 1 - pchisq((-2 * (as.numeric(DistPvalues %>% filter(Dist == "lnorm") %>% select(like)) - as.numeric(DistPvalues %>% filter(Dist == "gamma") %>% select(like)))), 1)
```
# From the statistical formal test we can conclude that gamma is better than log-normal, and weibull is better than gamma.

### Variable selection using backward selection
```{r}
Model1 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + age + bridgecrane + servo + gear + trashrack + slope + elevation, data = Data, dist = "weibull")
summary(Model1)

Model2 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + bridgecrane + servo + gear + trashrack + slope + elevation, data = Data, dist = "weibull")
summary(Model2)

Model3 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + servo + gear + trashrack + slope + elevation, data = Data, dist = "weibull")
summary(Model3)

Model4 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + servo + gear + trashrack + slope, data = Data, dist = "weibull")
summary(Model4)

Model5 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + servo + trashrack + slope, data = Data, dist = "weibull")
summary(Model5)

Model6 <- survreg(Surv(hour, Flood == 1) ~ 
                              backup + servo + slope, data = Data, dist = "weibull")
summary(Model6)
```
The most significant variable is slope. 45.4% decrease in the expected survival time for each one-unit increases in slope.

###

