---
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r}
library(sas7bdat)
library(dplyr)
library(reshape2)
library(ggplot2)
library(ggthemes)
library(survival)
library(survminer)
library(zoo)
library(flexsurv)
```

### Reading data
```{r}
Data <- read.sas7bdat("/Users/dauku/Desktop/Courses/2019Fall/Survival/Homework1_SA/hurricane.sas7bdat")
Data$reason <- as.factor(Data$reason)
Data$pumpid <- seq(1, nrow(Data))
Data[is.na(Data)] <- 0

Motor <- sapply(Data$reason, function(x) {
  if (x == 2) {
    return(1)
  } else {
    return(0)
  }
})

Data$survive <- Motor

```

### Process Data
```{r}
Hours12 = apply(Data[, 9:56], MARGIN = 1, FUN = function(h) {
  store = matrix(ncol = 48)
  for (i in seq(12, 48)) {
    Sum <- sum(h[(i-11):i])
    if (Sum == 12) {
      store[i] <- 1
    } else {
      store[i] <- 0
    }
  }
  return(store)
})

Hours12 <- t(Hours12)
Hours12[, 1:11] <- 0

DataMatrix <- as.matrix(Data)
New <- cbind(DataMatrix[, 1:8], Hours12, DataMatrix[, 57:60])
ColName <- colnames(Data)[1:60]

colnames(New) <- ColName

NewData <- as.data.frame(New)

DataLong <- reshape(data = NewData, varying = paste0("h", 1:48), v.names = "motor_working",
                    timevar = "time", idvar = "id", direction = "long", sep = "")

library(doBy)
DataLong <- orderBy(~ + id + time, data = DataLong)

library(plyr)
library(doMC)
registerDoMC()
DataLong <- ddply(.data = DataLong, .variable = c("id"),
                  .drop = TRUE, .parallel = TRUE, .fun = function(DF) {
                    DF$start <- c(0, head(DF$time, -1))
                    DF$stop <- DF$time
                    DF
                  })

Long <- DataLong %>%
  group_by(id) %>%
  slice(1:hour)

motor_working <- as.matrix(Long$motor_working)
ID <- as.matrix(Long$id)
j <- 1
indicator <- matrix(nrow = nrow(Long))
indicator[1] <- 1

for (i in seq(1, nrow(Long))) {
  if (i > 1) {
    if (ID[i] != ID[i-1]) {
      j <- 1
    }
    if (motor_working[i] == motor_working[i-1]) {
      indicator[i] <- j
    } else if ((motor_working[i] != motor_working[i-1]) & (ID[i] != ID[i-1])) {
      indicator[i] <- 1
    } else {
      j <- j + 1
      indicator[i] <- j
    }
  }
}

Long$indicator <- indicator

LongShort <- Long %>%
  group_by(id, indicator) %>% 
  filter(row_number()==1 | row_number()==n()) %>%
  ungroup() %>% 
  group_by(id) %>%
  mutate(stop = dplyr::lead(stop)) %>%
  ungroup()

LongShort <- LongShort %>%
  group_by(id, indicator) %>%
  filter(row_number()==1) %>%
  ungroup() %>% 
  dplyr::select(backup, age, bridgecrane, servo, gear, trashrack, slope, elevation, survive, hour, motor_working, id,
                start, stop, indicator)

LongShort$stop[is.na(LongShort$stop)] <- LongShort$hour[is.na(LongShort$stop)]

dplyr::rename(LongShort, motor = survive)
# lg <- function(x)c(NA, x[1:(length(x)-1)])
# library(data.table)
# ddt <- data.table(LongShort)
# LongShort <- ddt[,newstart := lg(start), by = c("id", "indicator")]
# 
# LongShort <- LongShort %>%
#   dplyr::select(backup, age, bridgecrane, servo, gear, trashrack, slope, elevation, survive, hour, time, motor_working, id,
#                 newstart, stop, indicator) %>%
#   group_by(id, indicator) %>%
#   filter(row_number() == n())
# 
# test <- LongShort %>%
#   group_by(id) %>%
#   mutate(newstart = lag(start, order_by = id))
# 
#   mutate(newstart = replace(newstart, start == 0, 0)) %>%
#   dplyr::select(backup, age, bridgecrane, servo, gear, trashrack, slope, elevation, survive, hour, time, motor_working, id,
#                 newstart, stop, indicator)
```

```{r}
# Variable selection
library(MASS)
stepAIC(coxph(Surv(hour, survive == 0) ~ backup + age + bridgecrane + servo + gear + trashrack + slope + elevation,
              data = Data))
```


Cox
```{r}
# Checking assumption
ph1 <- coxph(Surv(hour, survive == 0) ~ backup + age + bridgecrane + servo + gear + trashrack + slope + elevation,
             data = Data)

summary(ph1)

# proportional hazard test
ph1.zph.log <- cox.zph(ph1, transform = log)
log.table <- ph1.zph.log$table

ph1.zph.identity <- cox.zph(ph1, transform = identity)
identity.table <- ph1.zph.identity$table

pvalues <- cbind(log.table[, 3], identity.table[, 3])
pvalues <- data.frame(pvalues)
colnames(pvalues) <- c("log", "identity")
adjust <- c("met", "identity", "met", "log", "met", "met", "identity", "identity", NA)
pvalues$adjust <- adjust

# time dependent coefficient
ph1.tdc <- coxph(Surv(hour, survive == 0) ~ backup + age + bridgecrane + servo + gear + trashrack + slope + elevation +
                   tt(age) + tt(servo) + tt(slope) + tt(elevation), data = Data, 
                 tt = list(
                   function(x, time, ...){x*time},
                   function(x, time, ...){x*log(time)},
                   function(x, time, ...){x*time},
                   function(x, time, ...){x*time})
                 )
summary(ph1.tdc)
```

```{r}
# Time dependent variable 
sapply(LongShort, class)
LongShort$age <- as.numeric(LongShort$age)
LongShort$slope <- as.numeric(LongShort$slope)
LongShort$elevation <- as.numeric(LongShort$elevation)
LongShort$hour <- as.numeric(LongShort$hour)

ph.long <- coxph(Surv(start, stop, motor == 1) ~ backup + age + bridgecrane + servo + gear + trashrack + slope +
                   elevation + motor_working, data = LongShort)

summary(ph.long)

library(MASS)
stepAIC(coxph(Surv(hour, Motor == 1) ~ backup + age + bridgecrane + servo + gear + trashrack + slope + elevation + mortor_working
                   + t1(age) + t2(servo) + t1(slope) + t1(elevation), data = LongShort, 
                 t1 = function(x, time){x*time}, t2 = function(x, time){x*log(time)}
                 ))

```

# including both time dependent variable and coefficient
ph.long.both <- coxph(Surv(start, stop, survive == 0) ~ backup + age + bridgecrane + servo + gear + trashrack + slope +
                   elevation + motor_working + tt(age) + tt(servo) + tt(trashrack) + tt(slope), data = Long, 
                 tt = list(
                   function(x, time, ...){x*time},
                   function(x, time, ...){x*log(time)},
                   function(x, time, ...){x*time},
                   function(x, time, ...){x*time}))

# ph1.tdc <- coxph(Surv(hour, survive == 0) ~ backup + age + bridgecrane + servo + gear + trashrack + slope + elevation +
#                    tt(age) + tt(servo) + tt(trashrack) + tt(slope), data = Data, 
#                  tt = list(
#                    function(x, time, ...){x*time},
#                    function(x, time, ...){x*log(time)},
#                    function(x, time, ...){x*time},
#                    function(x, time, ...){x*time})
#                  )
summary(ph.long.both)
```

